---
title: "must nice eda"
output:
  html_document:
    df_print: paged
---

```{r setup, include = FALSE}
select_include = FALSE
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE
)

knitr::opts_knit$set(root.dir = here::here())
```

```{r}
#### read files & view them
library(plyr)
library(dplyr)
library(tidyverse)
library(lubridate)
library(readr)
library(magrittr)
library(plotly)

#setwd("~/Downloads/pf_visits_dump_hashed")

venue_info <- read.csv(file = '~/Downloads/pf_visits_dump_hashed/venues_info.csv')

Molly_Lane_Woodstock <- read.csv(file = '~/Downloads/pf_visits_dump_hashed/visits_Planet_Fitness_299_Molly_Lane_Woodstock_GA_United_States_2018-02-01_2019-02-01.csv')
Holcomb_Bridge_Road_Roswell <- read.csv(file = '~/Downloads/pf_visits_dump_hashed/visits_Planet_Fitness_1570_Holcomb_Bridge_Road_Roswell_Georgia_United_States_2018-02-01_2019-02-01.csv')
Alpharetta_Hwy_Roswell <- read.csv(file = '~/Downloads/pf_visits_dump_hashed/visits_Planet_Fitness_10790_Alpharetta_Hwy_Roswell_GA_30076_Roswell_GA_United_States_2018-02-01_2019-02-01.csv')
Highway_9_Milton <- read.csv(file = '~/Downloads/pf_visits_dump_hashed/visits_Planet_Fitness_13071_Highway_9_Milton_GA_United_States_2018-02-01_2019-02-01.csv')

```

```{r}
### clean data
data_clean <- function(gym_table) {
  
  gym_table <- gym_table %>%
  mutate(visit_start_time = as.POSIXct(visit_start_time),
         visit_end_time = as.POSIXct(visit_end_time)) %>% 
  mutate(visit_start_month = format(visit_start_time, format = "%Y-%m")) %>% 
  mutate(visit_start_week = floor_date(visit_start_time,"week",1)) %>% 
  left_join(venue_info %>% select(-X.), by = "venue_id") %>% 
  as_tibble()
}

Molly_Lane_Woodstock <- Molly_Lane_Woodstock %>% data_clean()
Holcomb_Bridge_Road_Roswell <- Holcomb_Bridge_Road_Roswell %>% data_clean()
Alpharetta_Hwy_Roswell <- Alpharetta_Hwy_Roswell %>% data_clean()
Highway_9_Milton <- Highway_9_Milton %>% data_clean()

```

### calculate the weights to see if the gym is really underperforming
It is, but not worse than Highway_9_Milton; also the visit/customer ratio is similar; the problem is n_customers.

Weekly
```{r}

weekly_weights <- function(gym_table) {
  
  gym_table_p <- gym_table %>%
    ## be sure to count the customer weight once per timeframe and the visits for each row
    group_by(visit_start_week, device_id, customer_weight) %>%
  summarise(visit_weight = sum(visit_weight)) %>% 
    group_by(visit_start_week) %>%
    summarise(n_customers = sum(customer_weight), 
              n_visits = sum(visit_weight)) %>% 
    summarise(median_weekly_customers = median(n_customers), median_weekly_visits = median(n_visits), visits_per_customer = median(n_visits) / median(n_customers)) %>% 
    ungroup() %>% 
    as_tibble()
}

Alpharetta_Hwy_Roswell_weekly <- Alpharetta_Hwy_Roswell %>% weekly_weights()
Holcomb_Bridge_Road_Roswell_weekly <- Holcomb_Bridge_Road_Roswell %>% weekly_weights()
Molly_Lane_Woodstock_weekly <- Molly_Lane_Woodstock %>% weekly_weights()
Highway_9_Milton_weekly <- Highway_9_Milton %>% weekly_weights()

rbind(Alpharetta_Hwy_Roswell = Alpharetta_Hwy_Roswell_weekly,
      Holcomb_Bridge_Road_Roswell = Holcomb_Bridge_Road_Roswell_weekly,
      Molly_Lane_Woodstock = Molly_Lane_Woodstock_weekly,
      Highway_9_Milton = Highway_9_Milton_weekly)


```

Monthly
```{r}

weekly_weights <- function(gym_table) {
  
  gym_table_p <- gym_table %>%
    ## be sure to count the customer weight once per timeframe and the visits for each row
    group_by(visit_start_month, device_id, customer_weight) %>%
  summarise(visit_weight = sum(visit_weight)) %>% 
    group_by(visit_start_month) %>%
    summarise(n_customers = sum(customer_weight), 
              n_visits = sum(visit_weight)) %>% 
    summarise(median_monthly_customers = median(n_customers), median_monthly_visits = median(n_visits), visits_per_customer = median(n_visits) / median(n_customers)) %>% 
    ungroup() %>% 
    as_tibble()
}

Alpharetta_Hwy_Roswell_p <- Alpharetta_Hwy_Roswell %>% weekly_weights()
Holcomb_Bridge_Road_Roswell_p <- Holcomb_Bridge_Road_Roswell %>% weekly_weights()
Molly_Lane_Woodstock_p <- Molly_Lane_Woodstock %>% weekly_weights()
Highway_9_Milton_p <- Highway_9_Milton %>% weekly_weights()

rbind(Alpharetta_Hwy_Roswell_p = Alpharetta_Hwy_Roswell_p,
      Holcomb_Bridge_Road_Roswell_p = Holcomb_Bridge_Road_Roswell_p,
      Molly_Lane_Woodstock_p = Molly_Lane_Woodstock_p,
      Highway_9_Milton_p = Highway_9_Milton_p)
```


```{r}
##Total
# Alpharetta_Hwy_Roswell_p <- Alpharetta_Hwy_Roswell %>% 
#   summarise(n_customers = sum(customer_weight), n_visits = sum(visit_weight))
# 
# Holcomb_Bridge_Road_Roswell_p <- Holcomb_Bridge_Road_Roswell %>% 
#   summarise(n_customers = sum(customer_weight), n_visits = sum(visit_weight))
# 
# Molly_Lane_Woodstock_p <- Molly_Lane_Woodstock %>% 
#   summarise(n_customers = sum(customer_weight), n_visits = sum(visit_weight))
# 
# Highway_9_Milton_p <- Highway_9_Milton %>% 
#   summarise(n_customers = sum(customer_weight), n_visits = sum(visit_weight))
# 
# 
# rbind(Alpharetta_Hwy_Roswell_p = Alpharetta_Hwy_Roswell_p,
#       Holcomb_Bridge_Road_Roswell_p = Holcomb_Bridge_Road_Roswell_p,
#       Molly_Lane_Woodstock_p = Molly_Lane_Woodstock_p,
#       Highway_9_Milton_p = Highway_9_Milton_p)

```

## Why is Alpharetta_Hwy_Roswell_p underperforming?

```{r}
### Trend over time
#Peformance in the better performing gyms is dropping but it does not answer the question so not relevant

# Highway_9_Milton %>% 
#   group_by(visit_start_week) %>% 
#   summarise(n_customers = sum(customer_weight), n_visits = sum(visit_weight)) %>% 
#   plot_ly(x = ~visit_start_week) %>% 
#   add_trace(y = ~n_visits) %>%  
#   add_trace(y = ~n_customers)
```

### check how far is each gym from home or work of users (median)
Take the median long and lat for each device
Do the distance of each from the gym
Do a weighted avg = distance * customer weight / sum of customers
Per week/month
```{r}
w_avg_distance <- function(gym_table) {
  
  w_avg_distance <- gym_table %>%
    ## Take the median long and lat for each device
  group_by(device_id) %>% 
  summarise(venue_lat = median(venue_lat),
            venue_long = median(venue_lng),
            customer_weight = median(customer_weight),
            med_home_lat = median(user_home_lat),
            med_home_long = median(user_home_long),
            med_work_lat = median(user_work_lat),
            med_work_long = median(user_work_long)
            ) %>% 
  ungroup() %>% 
  ## Do the distance of each from the gym
  mutate(distance_from_home = sqrt((med_home_lat - venue_lat)^2 + (med_home_long - venue_long)^2)) %>% 
  mutate(distance_from_work = sqrt((med_work_lat - venue_lat)^2 + (med_work_long - venue_long)^2)) %>% 
  ## chose the nearest - work or home
  rowwise() %>%
  mutate(distance_from_nearest = min(distance_from_home, distance_from_work, na.rm = T)) %>% 
  ungroup() %>% 
  ## Do a weighted avg = distance * customer weight / sum of customers
  summarise(w_avg = sum(distance_from_nearest*customer_weight)/sum(customer_weight))
}

Alpharetta_Hwy_Roswell_distance <- Alpharetta_Hwy_Roswell %>% w_avg_distance()
Holcomb_Bridge_Road_Roswell_distance <- Holcomb_Bridge_Road_Roswell %>% w_avg_distance()
Molly_Lane_Woodstock_distance <- Molly_Lane_Woodstock %>% w_avg_distance()
Highway_9_Milton_distance <- Highway_9_Milton %>% w_avg_distance()

rbind(Alpharetta_Hwy_Roswell_d = Alpharetta_Hwy_Roswell_distance,
      Holcomb_Bridge_Road_Roswell_d = Holcomb_Bridge_Road_Roswell_distance,
      Molly_Lane_Woodstock_d = Molly_Lane_Woodstock_distance,
      Highway_9_Milton_d = Highway_9_Milton_distance)
```

### Are Holcomb_Bridge_Road_Roswell and Highway_9_Milton_p compeating with Alpharetta_Hwy_Roswell?


